Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2015-01-27 Paper/ms.tex
A bit more discussion

One possible explanation for the large number of inferred signals that a
non-sinusoidal signal due to stellar activity is being modelled as several
periods \citep{astero}, and if the model were extended to include a ``stochastic''
oscillation \citep{gaussproc}, the number of periods detected may be reduced
substantially. With these kinds of models, the posterior distribution for $N$
can also be influenced by the prior for the amplitudes $A_i$. Many authors
assign independent broad priors to the amplitudes, and this causes the
``Occam's razor'' penalty for adding extra signals to be quite strong. Since we
use a hierarchical prior for the amplitudes, if some amplitudes are found to
be low, $\mu_A$ will become small. When $\mu_A$ is small, it is likely that any
extra signals will have small amplitudes, so the ``Occam's razor'' effect is
weaker. An example model fit for Gliese 581 is shown in
Figure~\ref{fig:gliese581}.

>>>>

One possible explanation for the large number of inferred signals that a
non-sinusoidal signal due to stellar activity is being modelled as several
periods \citep[e.g. as happens in asteroseismology when sinusoidal models are
used;][]{astero}, and if the model were extended to include a ``stochastic''
oscillation \citep[e.g.][]{gaussproc}, the number of periods detected may be reduced
substantially. Another contributing factor is the prior for the amplitudes.
With these kinds of models, the posterior distribution for $N$
can also be influenced by the prior for the amplitudes $A_i$. Many authors
assign independent broad priors to the amplitudes, and this causes the
``Occam's razor'' penalty for adding extra signals to be quite strong. Since we
use a hierarchical prior for the amplitudes, if some amplitudes are found to
be low, $\mu_A$ will become small. When $\mu_A$ is small, it is likely that any
extra signals will have small amplitudes, so the ``Occam's razor'' effect is
weaker. An example model fit for Gliese 581 is shown in
Figure~\ref{fig:gliese581}.
